Red wine exploratory data analysis by Siân Nadin
========================================================



```{r echo=FALSE, message=FALSE, warning=FALSE, packages}

# Load all of the packages that you end up using in your analysis in this code
# chunk.
#install.packages('ggplot2')
library(ggplot2)
#install.packages('gridExtra')
library(gridExtra)
#install.packages('dplyr')
#install.packages("tidyr")
#install.packages('reshape2')
install.packages("corrplot")
# The parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.


```

```{r echo=FALSE, Load_the_Data}
# Load the Data
red_wine <- read.csv('wineQualityReds.csv')
head(red_wine)
```
## About this dataset
This dataset is public available for research. The details are described in [Cortez et al., 2009].

P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis. Modeling wine preferences by data mining from physicochemical properties. In Decision Support Systems, Elsevier, 47(4):547-553. ISSN: 0167-9236.


### Description of attributes:
The dataset consists of 12 variables, with 1599 observations. 
The attributes are as follows:

   1 - *fixed acidity*: most acids involved with wine or fixed or nonvolatile 
   (do not evaporate readily)

   2 - *volatile acidity*: the amount of acetic acid in wine, which at too high 
   of levels can lead to an unpleasant, vinegar taste

   3 - *citric acid*: found in small quantities, citric acid can add 'freshness' 
   and flavor to wines

   4 - *residual sugar*: the amount of sugar remaining after fermentation stops, 
   it's rare to find wines with less than 1 gram/liter and wines with greater 
   than 45 grams/liter are considered sweet

   5 - *chlorides*: the amount of salt in the wine

   6 - *free sulfur dioxide*: the free form of SO2 exists in equilibrium between 
   molecular SO2 (as a dissolved gas) and bisulfite ion; it prevents microbial 
   growth and the oxidation of wine

   7 - *total sulfur dioxide*: amount of free and bound forms of S02; in low 
   concentrations, SO2 is mostly undetectable in wine, but at free SO2 
   concentrations over 50 ppm, SO2 becomes evident in the nose and taste of wine

   8 - *density*: the density of water is close to that of water depending on 
   the percent alcohol and sugar content

   9 - *pH*: describes how acidic or basic a wine is on a scale from 0 (very 
   acidic) to 14 (very basic); most wines are between 3-4 on the pH scale

   10 - *sulphates*: a wine additive which can contribute to sulfur dioxide gas 
   (S02) levels, wich acts as an antimicrobial and antioxidant

   11 - *alcohol*: the percent alcohol content of the wine

   Output variable (based on sensory data): 
   12 - *quality* (score between 0 and 10)
   
```{r}
summary(red_wine)
```



# Univariate Plots Section


First going to take a quick look at the distribution of alcohol percentage in 
the wine data set with the mean (in blue) and median (in black) plotted on the 
graph for reference.

```{r echo=FALSE, Univariate_Plots}
library(ggplot2)
ggplot(aes(x=quality), data=red_wine) + 
  geom_histogram(binwidth=1, color='black', fill='orange') +
    geom_vline(xintercept = median(red_wine$quality), linetype='longdash',
               alpha=.8) +
    geom_vline(xintercept = mean(red_wine$quality), linetype='longdash', 
               color='blue', alpha=.8) 
```

Most of the wines in the dataset are average quality wines with very few low and
high quality wines included in this dataset.
Due to the fact this data is primarily about average quality wines  it might be 
difficult to build a predictive model that will work acroos varying qualities of
wine.
May get a better understanding of the data set by plotting each of the 
variables to get a better idea of the spread of differences for the properties
included in this dataset.

```{r}
p1<-
  ggplot(aes(x = fixed.acidity), data = red_wine)+
        xlab("fixed acidity")+
        geom_histogram(colour="black", fill=I('blue'), binwidth = 0.5)
p2<-
  ggplot(aes(x = volatile.acidity), data = red_wine)+
        xlab("volatile acidity")+
        geom_histogram(colour="black", fill=I('blue'), binwidth = 0.05)
p3<-
  ggplot(aes(x = citric.acid), data = red_wine)+
        xlab("citric acid")+
        geom_histogram(colour="black", fill=I('blue'), binwidth = 0.05)
p4<-
  ggplot(aes(x = residual.sugar), data = red_wine)+
        xlab("residual sugar")+
        geom_histogram(colour="black", fill=I('blue'), binwidth = 0.4)
p5<-
  ggplot(aes(x = chlorides), data = red_wine)+
        geom_histogram(colour="black", fill=I('blue'), binwidth = 0.025)
p6<-
  ggplot(aes(x = free.sulfur.dioxide), data = red_wine)+
        xlab("free sulfur dioxide")+
        geom_histogram(colour="black", fill=I('blue'), binwidth = 4)
p7<-
  ggplot(aes(x = total.sulfur.dioxide), data = red_wine)+
        xlab("total sulfur dioxide")+
        geom_histogram(colour="black", fill=I('blue'), binwidth = 20)
p8<-
  ggplot(aes(x = density), data = red_wine)+
        geom_histogram(colour="black", fill=I('blue'), binwidth = 0.001)
p9<-
  ggplot(aes(x = pH), data = red_wine)+
        geom_histogram(colour="black", fill=I('blue'), binwidth = 0.05)
p10<-
  ggplot(aes(x = sulphates), data = red_wine)+
        geom_histogram(colour="black", fill=I('blue'), binwidth = 0.1)
p11<-
  ggplot(aes(x = alcohol), data = red_wine)+
        geom_histogram(colour="black", fill=I('blue'), binwidth = 0.25)

grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,p11,ncol=3)

```

Observation from data:
Normal distribution:pH, density and fixed acidity. 
* pH and density both look like they are close to a perfectly normal 
distribution. Likely that these qualities are well regulated during the 
production of wine.

Long tail: 
* The distribution of Residual Sugar is again positively skewed with high peaks 
at around 2.3 with many outliers present at the higher ranges
* For Chlorides also, we see a similar distribution like Residual Sugar.


Positively skewed:   
* Fixed Acidity is positively skewed.
* Free Sulphur Dioxide follows the same positively skewed long tailed patterns 
with some outliers in the high range.
* Sulphates also exhibit a similar long tailed distribution and doesn't have a 
large amount of outliers.
* Alcohol also follows a skewed distribution but here the skewness is less than 
that of Chlorides or Residual Sugars.

The distribution of Citric acid looks almost rectangular. Some higher values have no 
data at all

The distribution of Volatile acidity looks like Bimodal with two peaks around 
0.4 and 0.6.

*** Create total acidity variable which = fixed+volatile acidity and see if its normal dist
see how the pH is affected by the different acids present in the wine and if the overall pH affects the quality of the wine
Maybe plot pH and acidity on top of each other in same plot to see if there's any correlation.

Maybe citric acid leveks vary as different amounts are added to produce different flavours. 
things like pH must be specifically within a certain range to produce a good wine whereas there's 
more flexibility with levels of citric acid

Residual sugar and Chloride seems to have extreme outliers.

# Univariate Analysis

> **Tip**: Now that you've completed your univariate explorations, it's time to
reflect on and summarize what you've found. Use the questions below to help you
gather your observations and add your own if you have other thoughts!

### What is the structure of your dataset?

### What is/are the main feature(s) of interest in your dataset?

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

### Did you create any new variables from existing variables in the dataset?

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?


# Bivariate Plots Section
```{r}
library(corrplot)
corrplot(M, method="circle")

```

> **Tip**: Based on what you saw in the univariate plots, what relationships
between variables might be interesting to look at in this section? Don't limit
yourself to relationships between a main output feature and one of the
supporting variables. Try to look at relationships between supporting variables
as well.

```{r echo=FALSE, Bivariate_Plots}

```

# Bivariate Analysis

> **Tip**: As before, summarize what you found in your bivariate explorations
here. Use the questions below to guide your discussion.

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

### What was the strongest relationship you found?


# Multivariate Plots Section

> **Tip**: Now it's time to put everything together. Based on what you found in
the bivariate plots section, create a few multivariate plots to investigate
more complex interactions between variables. Make sure that the plots that you
create here are justified by the plots you explored in the previous section. If
you plan on creating any mathematical models, this is the section where you
will do that.

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

> **Tip**: You've done a lot of exploration and have built up an understanding
of the structure of and relationships between the variables in your dataset.
Here, you will select three plots from all of your previous exploration to
present here as a summary of some of your most interesting findings. Make sure
that you have refined your selected plots for good titling, axis labels (with
units), and good aesthetic choices (e.g. color, transparency). After each plot,
make sure you justify why you chose each plot by describing what it shows.

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection

> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!